\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.15in}
 \addtolength{\textwidth}{0.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\vspace{0pt}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Paolo Araneta} \\[2mm]
    \footnotesize \raisebox{-0.1\height}
  \ \underline{(+63) 926-2355-926} \hspace{0.2em}\textbar\hspace{0.2em}
  {\  \underline{paoloaraneta008@gmail.com}} \hspace{0.2em}\textbar\hspace{0.2em}
  {\ \underline{\href{https://www.linkedin.com/in/paoloaraneta/}{linkedin.com/in/paoloaraneta}}} \hspace{0.2em}\textbar\hspace{0.2em}
  {\ \underline{\href{https://github.com/Aytsuu}{github.com/Aytsuu}}}
    \vspace{-8pt}
    \vspace{12pt}
\end{center}

 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cebu Technological University}{Expected July 2026}
      {Bachelor of Science in Information Technology
      }{Cebu City, Philippines}
  \resumeSubHeadingListEnd
    \vspace{-12pt}
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{   
      \textbf{Languages}{: Python, C\#, Javascript (Typescript), SQL} \\[1mm]
      \textbf{Frameworks}{: FastAPI, Django, Flask, .NET, React, Node.js} \\[1mm]
      \textbf{Tools}{: Git, Github, Docker, REST APIs, PostgreSQL, Redis} \\[1mm]
      \textbf{Cloud \& DevOps}{: Supabase, CI/CD Pipelines, Dockerized Deployments} \\[1mm]
    }}
 \end{itemize}
 \vspace{-16pt}
 \vspace{3pt}

%-----------Experience---------------
\section{Experience}
    \resumeSubHeadingListStart
      \resumeSubheading{Software Engineer Intern}{Feb 2026 -- June 2026}{Dinnox IT Solutions}{Cebu City, Philippines} 
        \resumeItemListStart
          \resumeItem{Led the development of a client-based website, implemented a structured monolithic architecture, and designed user workflows.}
          \resumeItem{Fixed a backend bug that heavily affected the development of interns and senior developers.}
          \resumeItem{Increased team productivity by introducing automation tools, such as leveraging agentic engineering in their workflows.}
        \resumeItemListEnd
      \resumeSubheading{Technical Training Instructor}{Aug 2025 -- Oct 2025}{Barangay San Roque (Ciudad)}{Cebu City, Philippines} 
        \resumeItemListStart
          \resumeItem{Served as a student trainer for the BarangayConnect Training Program, empowering \textbf{50+} local government workers through hands-on digital literacy training.}
          \resumeItem{Introduced and demonstrated key features of the barangay system, showcasing its benefits to non-technical residents and staffs.}
          \resumeItem{Conducted practical training sessions to assess and improve participants' computer literacy and system usage skills.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-12pt}

%-----------PROJECTS-----------

\section{Projects} 
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Orca} $|$ \emph{Python, Astro, React, Redis, Supabase, Docker}}{}
      \resumeItemListStart
        \resumeItem{Developed an AI-powered solution that turns real-time conversations into structured project plans so teams never loses sight of their project's finish line.}
        \resumeItem{Contributed to the development of this project's Minimum Viable Product within 6 days as Full Stack.}
      \resumeItemListEnd
    \vspace{-20pt}
    \resumeProjectHeading{\textbf{Findmyfiles} $|$ \emph{Python, C\#}}{}
      \resumeItemListStart
        \resumeItem{Built a searchable memory for Windows desktop files using Gemini Embedding 2 for multimodal data retrieval and embedded it with a vector database.}
      \resumeItemListEnd
    \vspace{-20pt}
    \resumeProjectHeading{\textbf{Hyperlocal Circular Economy Platform} $|$ \emph{React, FastAPI, Supabase, Docker}}{}
      \resumeItemListStart
        \resumeItem{Developed an application to divert food wastes from landfill, contributing to environmental wellness while fostering commnuity resilience.}
        \resumeItem{Integrated an AI inference automation for food waste posting via images using gemini cloud LLM models.}
      \resumeItemListEnd
    \vspace{-20pt}
    \resumeProjectHeading
      {\textbf{Barangay Management System} $|$ \emph{React, Django, Docker, SQL}}{}
      \resumeItemListStart
        \resumeItem{Implemented an automated Know Your Customer (KYC) verification and assessment for resident registration.}
        \resumeItem{Synchronized dual databases to ensure consistent real-time data access.}
        \resumeItem{Set up CI/CD pipelines with GitHub Actions for integration testing and continuous delivery via Render and Supabase services.}
      \resumeItemListEnd
    \vspace{-20pt}
    \resumeProjectHeading
      {\textbf{Face Recognition Profiling} $|$ \emph{React, Flask, NoSQL}}{}
      \resumeItemListStart
        \resumeItem{Developed a biometric profiling application using the FaceNet model for high-accuracy face recognition and Flask-SocketIO to enable real-time, bidirectional communication.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}



\vspace{-15pt}



\end{document}
